Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-26 snapshot_system/fast14_evaluation.tex
upate

 \subsection{Effectiveness of Approximate Deletion}
 \begin{figure}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions}
     \label{fig:leakage}
 \end{figure}

Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
given $\Delta u/u=0.025$,
while the top solid line represents the actual leakage measured during the experiment 
with the same $\Delta u/u=0.025$ setting for summary vectors.
After 9 snapshot deletions, the actual leakage ratio reaches 0.0018 and this means that
there is only 1.8MB space leaked for every 1GB of stored data, it is also obvious that
the leakage grows linearly as we expect. 
We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.
As this value increases, larger summary vectors are generated thus results in a decrease on the
false-positive ratio, therefore less amount of unused chunks are misjudged.

>>>>

 \subsection{Effectiveness of Approximate Deletion}

 \begin{figure}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}

Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
given $\Delta u/u=0.025$,
while the top solid line represents the actual leakage measured during the experiment 
with the same $\Delta u/u=0.025$ setting for summary vectors.
After 9 snapshot deletions, the actual leakage ratio reaches 0.0018 and this means that
there is only 1.8MB space leaked for every 1GB of stored data, it is also obvious that
the leakage grows linearly as we expect. 
% We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.
% As this value increases, larger summary vectors are generated thus results in a decrease on the
% false-positive ratio, therefore less amount of unused chunks are misjudged.
